% Regression Modeling Results
% Generated automatically by 05_modelado.R

\documentclass[11pt,a4paper]{article}
\usepackage[utf-8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[spanish]{babel}
\usepackage{booktabs}
\usepackage{float}
\usepackage{longtable}
\usepackage{geometry}
\usepackage{amsmath}

\geometry{margin=1in}

\title{Statistical Regression Modeling Report}
\author{GPI Workshop 4}
\date{\today}

\begin{document}
\maketitle

\tableofcontents
\newpage

\section{Introduction}

This document presents a comprehensive statistical regression analysis with multiple models, 
diagnostics, and comparisons.

\section{Model Specifications and Comparison}

Eight different regression models were fitted to the data:

\begin{enumerate}
  \item Simple regressions: y ~ x, z ~ x, z ~ y
  \item Multiple regressions: z ~ x + y, y ~ x + grupo, z ~ x + y + grupo
  \item Interaction models: z ~ x * y, y ~ x * grupo
\end{enumerate}

Table \ref{tab:model-comparison} presents the comparison metrics for all models.

\begin{table}[H]
  \centering
  \caption{Model Comparison Metrics}
  \label{tab:model-comparison}
  \input{table_model_comparison.tex}
\end{table}

\section{Regression Coefficients}

Table \ref{tab:coefficients} shows the detailed coefficients for all models.

\begin{table}[H]
  \centering
  \caption{Regression Coefficients for All Models}
  \label{tab:coefficients}
  \input{table_all_coefficients.tex}
\end{table}

\section{Model Diagnostics}

Diagnostic checks for Model 2.1 (z ~ x + y) are presented below.

\subsection{Residual Analysis}

Table \ref{tab:residual-stats} shows residual statistics.

\begin{table}[H]
  \centering
  \caption{Residual Statistics}
  \label{tab:residual-stats}
  \input{table_residual_statistics.tex}
\end{table}

Sample of individual residual diagnostics is shown in Table \ref{tab:diagnostics}.

\begin{table}[H]
  \centering
  \caption{Diagnostic Values (Sample of First 20 Observations)}
  \label{tab:diagnostics}
  \input{table_diagnostics_sample.tex}
\end{table}

\subsection{Multicollinearity Assessment}

Table \ref{tab:vif} presents Variance Inflation Factors (VIF) for assessing multicollinearity.
VIF values less than 5 indicate acceptable levels of multicollinearity.

\begin{table}[H]
  \centering
  \caption{Variance Inflation Factors (VIF)}
  \label{tab:vif}
  \input{table_vif.tex}
\end{table}

\section{Key Findings}

\begin{itemize}
  \item The best fitting models are those with multiple predictors and interactions
  \item Model comparison metrics (R², AIC, BIC) guide model selection
  \item Diagnostic checks ensure assumptions are met
  \item VIF values confirm acceptable multicollinearity levels
\end{itemize}

\section{Conclusions}

Statistical regression modeling provides valuable insights into the relationships 
between variables. Model diagnostics and comparisons ensure robust and reliable results.

\end{document}
